---
title: "Weight of Fish"
author: "Nicole Orizino"
date: "Spring 2021"
output: 
  html_document:
    number_sections: true
    toc: true
---


```{r include=FALSE,echo=FALSE}
require(tigerstats)
require(tidyverse)
```

# Fishdata chunk
```{r}
Fishdata=read.csv(file="Fish.csv")
```



# Introduction

<!--In this section you explain what you are trying to show.  Where did the data come from?  What is the research or other question you are trying to answer?!-->

## Build the best regression model you can that predicts the weight of perch
## Using only two predictor variables  

# Perch

## Methods

<!--Decide on your methods:  use "variable analysis" or other appropriate descriptors.  Make sure to choose at least one graphical method and at least one numerical method.!-->

```{r}
Perchdata=filter(Fishdata,Species=="Perch")
Perchdata = subset (Perchdata, select = -Species)
```



## Inferential Results

```{r}
library(leaps)
regsubsets.out <-
    regsubsets(Weight ~ .,
               data = Perchdata,
               nbest = 1,       # 1 best model for each number of predictors
               nvmax = NULL,    # NULL for no limit on number of variables
               force.in = NULL, force.out = NULL,
               method = "exhaustive")

summary.out <- summary(regsubsets.out)
as.data.frame(summary.out$outmat)
library(car)
subsets(regsubsets.out,statistic="adjr2",legend="bottomright",main="Adjusted R^2")
```
  
##Which is best??  

The best model is the model that uses two variables: H and W.

```{r}
which.max(summary.out$adjr2)
```
```{r}
summary.out$which[3,]
```

```{r}
best.model <- lm(Weight~Height+Width,data=Perchdata)
summary(best.model)
fullup <- lm(Weight~.,data=Perchdata)
```

The P-Value here is extremely small, meaning that this model was not made by chance, its an excellent fit.

```{r}
anova(fullup,best.model)
```
The P-Value is 0.879, it is a little bigger size P-VAlue meaning that there is really no difference between using the model with all the data vs the model with only 2 variables.

<!--State hypothesis clearly.  Make sure your discussion of the inferential test covers all the aspects that the test output produces, such as test statistic, p-value etc.  Make a decision about the null hypothesis, explain the assumptions on which the selected test/procedure was based, and why the chosen procedure satisfys the assumptions and is appropriate to answer the research question!-->



# Bream


## Methods

<!--Decide on your methods:  use "variable analysis" or other appropriate descriptors.  Make sure to choose at least one graphical method and at least one numerical method.!-->

```{r}
Breamdata=filter(Fishdata,Species=="Bream")
Breamdata = subset (Breamdata, select = -Species)
```



## Inferential Results

```{r}
library(leaps)
regsubsets.out <-
    regsubsets(Weight ~ .,
               data = Breamdata,
               nbest = 1,       # 1 best model for each number of predictors
               nvmax = NULL,    # NULL for no limit on number of variables
               force.in = NULL, force.out = NULL,
               method = "exhaustive")

summary.out <- summary(regsubsets.out)
as.data.frame(summary.out$outmat)
library(car)
subsets(regsubsets.out,statistic="adjr2",legend="bottomright",main="Adjusted R^2")
```

## Inferential Results


```{r}
library(leaps)
regsubsets.out <-
    regsubsets(Weight ~ .,
               data = Breamdata,
               nbest = 1,       # 1 best model for each number of predictors
               nvmax = NULL,    # NULL for no limit on number of variables
               force.in = NULL, force.out = NULL,
               method = "exhaustive")

summary.out <- summary(regsubsets.out)
as.data.frame(summary.out$outmat)
library(car)
subsets(regsubsets.out,statistic="adjr2",legend="bottomright",main="Adjusted R^2")
```
  
## Which is best??  

The best model is the model that uses 3 variables: L1, H and W.

```{r}
which.max(summary.out$adjr2)
```
```{r}
summary.out$which[3,]
```

```{r}
best.model <- lm(Weight~Length2+Height,data=Breamdata)
summary(best.model)
fullup <- lm(Weight~.,data=Breamdata)
```

```{r}
anova(fullup,best.model)
```


The P-Value is 0.5805 it is a big size as well, meaning that there is a no difference difference between using the best model that uses 3 variables vs the best model that uses only 2 variables.


<!--State hypothesis clearly.  Make sure your discussion of the inferential test covers all the aspects that the test output produces, such as test statistic, p-value etc.  Make a decision about the null hypothesis, explain the assumptions on which the selected test/procedure was based, and why the chosen procedure satisfys the assumptions and is appropriate to answer the research question!-->



# Smelt

## Methods

<!--Decide on your methods:  use "variable analysis" or other appropriate descriptors.  Make sure to choose at least one graphical method and at least one numerical method.!-->

```{r}
Smeltdata=filter(Fishdata,Species=="Smelt")
Smeltdata = subset (Smeltdata, select = -Species)
```



## Inferential Results

```{r}
library(leaps)
regsubsets.out <-
    regsubsets(Weight ~ .,
               data = Smeltdata,
               nbest = 1,       # 1 best model for each number of predictors
               nvmax = NULL,    # NULL for no limit on number of variables
               force.in = NULL, force.out = NULL,
               method = "exhaustive")

summary.out <- summary(regsubsets.out)
as.data.frame(summary.out$outmat)
library(car)
subsets(regsubsets.out,statistic="adjr2",legend="bottomright",main="Adjusted R^2")
```

## Inferential Results


```{r}
library(leaps)
regsubsets.out <-
    regsubsets(Weight ~ .,
               data = Smeltdata,
               nbest = 1,       # 1 best model for each number of predictors
               nvmax = NULL,    # NULL for no limit on number of variables
               force.in = NULL, force.out = NULL,
               method = "exhaustive")

summary.out <- summary(regsubsets.out)
as.data.frame(summary.out$outmat)
library(car)
subsets(regsubsets.out,statistic="adjr2",legend="bottomright",main="Adjusted R^2")
```
  
## Which is best??  
The best model is the one tha uses 4 variables, L1, L2, H, and W.

```{r}
which.max(summary.out$adjr2)
```
```{r}
summary.out$which[3,]
```

```{r}
best.model <- lm(Weight~Length2+Width,data=Smeltdata)
summary(best.model)
fullup <- lm(Weight~.,data=Smeltdata)
```

```{r}
anova(fullup,best.model)
```

The P-Value is 0.2521 it is too big to say that there is a difference between using the best model with 4 variables vs the best model with only 2 variables. 


<!--State hypothesis clearly.  Make sure your discussion of the inferential test covers all the aspects that the test output produces, such as test statistic, p-value etc.  Make a decision about the null hypothesis, explain the assumptions on which the selected test/procedure was based, and why the chosen procedure satisfys the assumptions and is appropriate to answer the research question!-->


# Discussion and Conclusion

<!--Discussion and conclusion here.  If you found a relationship be sure to consider whether the relationship occurs because one of the variavbles causes the other, or whether they perhasps are related for some other reason.  Watch the chapter 6 videos from the GeorgeTown videos collection.!-->

Based off the automatic selection of the variables in every case, it shows that there is no difference between using the model with two variables vs using the model with all variables. This was identified through the graphical depiction of the adjusted R-squared as well as the P-values.
In conclusion when comparing the P-values of the two variable models, the P-values were so small that we reject the Null Hypothesis that these models are beneficial of predicting the weight of fish.
And the P-values associated with the anovas were large and therefore showed that we failed to reject the Null Hypothesis, meaning that there is no difference  between using the model with two variables vs using the model with fullup variables.






